\begin{thebibliography}{}
\bibitem{stat1} 
L. Martinelli e L. Baldini,
\textit{Misure ed analisi dei dati: introduzione al laboratorio di fisica}. 
Edizioni ETS, 4a ed Settembre 2009.
\bibitem{stat2} 
R. Giuliano, \textit{Argomenti di probabilità e statistica}. Springer, 2011.
\bibitem{sec} 
S. Katzenbeisser e F. Petitcolas, \textit{Defining Security in Steganographic Systems}, in \textit{Proceedings of SPIE}, \textit{Security and Watermarking of Multimedia Contents IV}. International Society for Optical Engineering, 2002, pp. 50-56.
\bibitem{simmons}
G. Simmons, \textit{The Prisoners' Problem and the Subliminal Channel}, in \textit{Advances in Cryptology}. Plenum Press, 1984, pp. 51-67.
\bibitem{approach}
C.Cachin, \textit{An Information-Theoretic Model for Steganography}, in \textit{Information Hiding: Second International Workshop}. vol. 1525, Springer, 1998, pp. 306-318.
\bibitem{zoller}
J. Z\"oller et al., \textit{Modeling the Security of Steganographic Systems}, in \textit{Information Hiding: Second International Workshop}, vol. 1525, Springer, 1998, pp. 306-318.
\bibitem{fried1}
J. Fridrich e M. Goljan, \textit{Practical Steganalysis of digital images – State of the Art}, in \textit{Proceedings of SPIE, Security and Watermarking of Multimedia Contents IV}, International Society for Optical Engineering, 2002, pp. 1-13.
\bibitem{fried2}
J. Fridrich, M. Goljan e R. Du, \textit{Reliable detection of LSB steganography in color and grayscale images}, in \textit{Proceedings of 2001 ACM workshop on Multimedia and Security: new challenges}, ACM press, 2001, pp. 27-30.
\bibitem{chisq}
A.Westfeld e A. Pfitzman, \textit{Attacks on steganographic System. Breaking the Steganographic Utilities EzStego, Jsteg, Steganos and S-Tools and some lessons learned}, in \textit{Proceedings of third International Information Hiding Workshop}, vol. 1768, Springer, 1999, pp. 67-76.
\bibitem{survey}
B. Lin, J. He, J. Huang e Y.Q. Shi, \textit{A survey on image steganography and steganalysis}, in \textit{Journal of Information
Hiding and Multimedia Signal Processing}, vol. 2, no. 2, 2011, pp. 142-172.
\bibitem{survey2}
Y.J. Chanu, Kh.M. Singh e T. Tuithung, \textit{Image Steganography and Steganalysis: A Survey}, in \textit{International journal of Computer Applications}, vol. 52, no. 2, 2012.
\bibitem{seeingTheUnseen}
N.F. Johnson e S. Jajodia, \textit{Exploring steganography: seeing the unseen}, in \textit{IEEE Computer}, vol. 31, no. 2, pp. 26-34, 1998.
\bibitem{experts}
T. Aura, \textit{Invisible Communication}, in \textit{Technical report of Helsinki Univ. of Technology}, EET, 1995.
\bibitem{warfare}
H. Wang e S. Wang, \textit{Cyber Warfare: Steganography  vs Steganalysis}, in \textit{Communications of the ACM}, vol. 47, no 10, pp. 76-82, 2004.
\bibitem{provos}
N. Provos, \textit{Defending Against Statistical Steganalysis}, in \textit{10th USENIX Secutiry Symposium}, 2001.
\bibitem{sup}
R. Chandramouli e N. Memon, \textit{Analysis of LSB based Image Steganography Techniques}, in \textit{Proceedings of ICIP}, 2001.
\bibitem{mat1}
J. Mielikainen, \textit{Lsb matching revisited}, in \textit{IEEE Signal Processing Letters}, vol. 13, no. 5, pp. 285-287,
2006.
\bibitem{mat2}
X. Li, B. Yang, D. Cheng, e T. Zeng, \textit{A generalization of lsb matching}, in \textit{IEEE Signal Processing
Letters}, vol. 16, no. 2, pp. 69-72, 2009.
\bibitem{sito}
ESET Research, \textit{Readers of popular websites targeted by stealthy Stegano exploit kit hiding in pixels of malicious ads}, in \textit{ESET Research Papers}, 2016.
\bibitem{improved}
X. Luo, B. Liu e F. Liu, \textit{Improved RS method for detection of LSB steganography}, in \textit{Computational Science and Its Applications -- ICCSA 2005: International Conference, Singapore, Proceedings}, Springer Berlin Heidelberg, 2005, pp. 508-516.
\end{thebibliography}