% !TEX root = main.tex
\chapter{Objectives}\label{sec:methods} %and goals of ReviewerNet}

The aim of ReviewerNet is to facilitate the reviewer selection process in the academic domain. While designing ReviewerNet, we took into account the characteristics of the \emph{users}, the users' \emph{tasks}, and the \emph{data} the users are working with \cite{MiAi14}. 

The \emph{users} of ReviewerNet are researchers, and in particular those playing the role of journal editors, associate editors, and members of IPCs of big conferences, in any field of research. Their \emph{task} is searching for reviewers for a submitted paper: this involves searching the literature for key papers and authors in the field; evaluating the candidates' research interests and their evolution over time; and assessing the candidates' conflict of interest with respect to the submitting authors and other reviewers. ReviewerNet supports all these subtasks, by visualizing the literature related with a topic, the career of relevant researchers in the field, and the relationships among researchers. 

The data pertain to three types of entities: \emph{papers}, \emph{researchers}, and \emph{citations}. The data attributes are both quantitative and qualitative, and the time dimension is central. 

In ReviewerNet, the attributes of a paper which are visualized are its \emph{citation count} -- the number of papers citing it -- as well as standard \emph{bibliographic attributes} -- title, authors, publication year, venue. Papers are related through \emph{direct citations}. 

Researchers have two attributes in ReviewerNet: relevance and conflict of interest. We define a researcher's \emph{relevance} as a reviewer according to the authorship of relevant papers. The concept of relevance can be tuned according to the user needs (e.g., looking for highly-specialized reviewers, as opposed to generalists). The second attribute of researchers is their \emph{conflict of interest}, with either the submitting authors or other reviewers. We model the conflict of interest after \emph{co-authorship} relations: two researchers have a conflict of interest if they have papers in common. We let the degree of conflict, and hence the availability as a reviewer, be modulated according to the number of papers in common, and the years passed since the last co-authored paper, again according to the user intent. 

The following section details the notation used in the rest of the paper, and the formal definition of paper and researcher attributes. 

\section{Notation}
\label{sec:notation}
Let $\mathcal{P}$ denote the set of papers in a reference dataset, %, with cardinality $\vert \mathcal{P} \vert$, 
and let $\mathcal{P}_{V} \subseteq \mathcal{P}$ be the set of papers relevant to a submission. %, with $\mathcal{P}_{V} \subseteq \mathcal{P}$. The set $\mathcal{P}_{V}$ of relevant papers 
$\mathcal{P}_{V}$ is built by the users starting from a small number of seed papers of their choice (cf. Chapter \ref{sec:demonstration}).%, through the graph expansion functionalities offered by the Paper Network visualization.   

A paper $p \in \mathcal{P}_{V}$ is marked as \emph{selected}, if it is considered as a key paper by the user; we denote by $\mathcal{P}_{S}$ the set of selected papers, with $\mathcal{P}_{S} \subseteq \mathcal{P}_{V} \subseteq \mathcal{P}$. 

If $\mathcal{C}(p)$ is the set of papers citing $p$, the \emph{citation count} $c(p)$ is its cardinality: $c(p) = \vert \mathcal{C}(p) \vert$.

Let $\mathcal{A}(p)$ be the set of authors of a given paper $p$, and $\mathcal{R}$ the set of authors of papers in $\mathcal{P}$. 
%, and $\mathcal{R}_{V}$ be the set of authors of papers in $\mathcal{P}_{V}$: $\mathcal{R}_{V} = \{r \in \mathcal{R} \ s.t. \ \exists \ p \in \mathcal{P}_V : r \in \mathcal{A}(p)\}$. 
Then, the set $\mathcal{R}_C \subseteq \mathcal{R}$ of \emph{candidate reviewers} is given by the set of researchers who authored a selected paper: $$\mathcal{R}_{C} = \{r \in \mathcal{R} \ s.t. \ \exists \ p \in \mathcal{P}_S : r \in \mathcal{A}(p)\}$$ %It holds that $\mathcal{R}_C \subseteq \mathcal{R}_{V} \subseteq \mathcal{R}$.  
%
For a candidate reviewer $r$, let $\mathcal{P}_{S}|_{r}$ be the set of papers in $\mathcal{P}_{S}$ authored by $r$. Then, the \emph{relevance score} $s(r)$ of the candidate reviewer $r$ is defined as a weighted sum of the number of selected and non-selected papers in $\mathcal{P}_V$ authored by $r$: $$s(r) = \alpha \vert \mathcal{P}_{S}|_{r} \vert + \beta \vert \{\mathcal{P}_{V} - \mathcal{P}_{S}\}|_{r}\vert$$ with $\alpha$ and $\beta$ real-valued coefficients summing up to one. We set $\alpha = 0.7$ and $\beta = 0.3$ as default parameters. The set of candidate reviewers will be visualized in the Researcher Timeline in order of their relevance; relevance will also define the dimension of nodes in the Researcher Network.

Finally, $\mathcal{CA}(r)$ denotes the set of co-authors of a researcher $r$, or, in other words, the set of researchers who have a conflict with him/her. 